
\appendix

\chapter{List of Requirement Questions}

\section{Interview}[h]
1. Can you tell us about your experience with building online management systems for businesses?		\\								
2. What are the key features that you think are essential for an effective online coffee shop management system?			\\							
3. How would you approach designing the user interface of the website to make it appealing and easy to use for customers?	\\									
4. Can you describe your experience with payment gateway integration and how you would handle payment processing for the online coffee shop?		\\			5. How would you ensure the security of customer information and payment data on the website?				\\						
6. Can you explain how you would implement the order approval process for sales staff and what criteria they would use to approve or cancel orders?\\			7. How would you approach managing promotional programs for the coffee shop, and what strategies would you use to attract customers?\\										
8. Can you describe how you would handle product inventory and supplier management within the system?		\\								
9. How would you ensure that the website is optimized for search engines and that customers can easily find the products they are looking for?	\\									
10. How would you handle customer service inquiries and ensure that customers are satisfied with their shopping experience on the website?	\\									
11. How would you ensure that the website is mobile-friendly and responsive for customers accessing it from their mobile devices?	\\									
12. Can you describe your experience with integrating third-party services or APIs into an online management system, and how would you utilize this in the coffee shop management system?			\\							
13. How would you approach designing a system for managing and tracking orders, from the point of order placement to delivery?	\\									
14. How would you ensure that the website is scalable and can handle a large volume of traffic and transactions during peak periods?		\\								
15. How would you implement a system for managing customer reviews and feedback, and how would you use this to improve the coffee shop's products and services?					\\					
16. Can you describe how you would handle shipping and delivery logistics, and how this would be integrated into the order management system?\\										
17. How would you ensure that the website is compliant with data privacy and protection regulations, such as GDPR or CCPA?			\\							
18. Can you explain how you would handle pricing and discount management within the system, and how this would be reflected in the shopping cart and checkout process?								\\		
19. How would you implement a system for generating reports and analytics to provide insights into sales performance and customer behavior on the website?\\	


\section{Questionnaire}

\textbf{1. Which of the following features would be essential for an online coffee shop management system?}

a. Online payment processing

b. Product search and filtering

c. Customer service support

d. All of the above

\medskip

\textbf{2. What is the purpose of the order approval process in the coffee shop management system?}

a. To confirm the accuracy of order information

b. To manage promotional programs

c. To handle product returns or exchanges

d. None of the above

\medskip

\textbf{3. Which of the following roles would be responsible for managing promotional programs?}

a. Sales staff

b. Posting staff

c. Warehouse managers

d. Customer service staff

\medskip

\textbf{4. How would the online coffee shop management system handle payment processing?}

a. Customers can only pay online

b. Customers can only pay in-person

c. Customers can choose to pay online or in-person

d. The system does not handle payment processing

\medskip

\textbf{5. What information can registered users view on the website?}

a. Order history and shopping cart

b. Personal information

c. Product inventory

d. All of the above

\medskip

\textbf{6. How would the system handle product inventory management?}

a. Warehouse managers can add, delete, or edit products in the system and add new products

b. Sales staff can manage promotional programs

c. Posting staff can manage blog posts and add, delete, or edit content

d. None of the above

\medskip

\textbf{7. How would the website handle customer reviews and feedback?}

a. There is no system for managing customer reviews and feedback

b. Customers can leave reviews and feedback, but it will not be used to improve products and services

c. The system would manage customer reviews and feedback and use it to improve products and services

d. Customer reviews and feedback would be handled by the customer service staff

\medskip

\textbf{8. Which of the following roles would have access to manage personnel and view system statistics?}

a. Sales staff

b. Posting staff

c. Warehouse managers

d. Administrators

\medskip

\textbf{9. How would the website ensure the security of customer information and payment data?}

a. By using a secure payment gateway

b. By encrypting customer information and payment data

c. By using multi-factor authentication for user accounts

d. All of the above

\medskip

\textbf{10. How would the website handle shipping and delivery logistics?}

a. Shipping and delivery logistics are not handled by the website

b. Warehouse managers would handle shipping and delivery logistics

c. The system would integrate shipping and delivery logistics into the order management process

d. Shipping and delivery logistics would be handled by the customer service staff
