\section{Introduction} %1.1 Gioi thiệu đề tài
Provide customers with a place to buy high-quality and diverse coffee products, while helping the store efficiently manage sales. The website will have basic functions such as product search, ordering, payment, order management, product management, and other relevant information about the store. Especially, the website will have a beautiful design, user-friendly interface, and optimized online shopping experience for customers. Coffee products are diverse, from pure coffee, filter and coffee makers to various coffee drinks. In addition, the website also has the function of online ordering and home delivery, helping customers save time and effort when shopping. This topic aims to apply the knowledge learned about requirements analysis, web development, database design, and user experience optimization to build a professional and effective e-commerce website.
\section{System Description} %1.2 Đặc tả hệ thống
An online coffee shop management system that provides customers with a place to shop for high-quality coffee-related products, while helping store owners manage sales efficiently. \\
• The website will display the store's featured products, along with many attractive promotional programs. In addition, users can search and filter products according to their needs, contact the store's customer service staff if they have any requests or questions. Users can also read blog posts about coffee processing, storage, home brewing instructions, and coffee culture.\\
• When users want to place an order, they do not need to register an account. After placing an order, they can choose to pay online or in-person.\\
• When they have an account, users can change their personal information. In addition, they can view their order history and shopping cart. Only registered users can view their order history.\\
• After users have successfully placed an order, the system will send the order to the sales staff to approve the order. The sales staff will check the accuracy of the order information to confirm or cancel the order. In addition, sales staff can manage promotional programs.\\
• Posting staff can manage blog posts and add, delete, or edit content.\\
• Customer service staff can support customers and answer their questions.\\
• Warehouse managers can add, delete, or edit products in the system and add new products. They can also manage suppliers.\\
• Administrators can do everything that employees can do, and also manage personnel and view system statistics.
\section{Purpose and Scope} %1.3 Phạm vi đề tài

\subsection{Limitations on object and function} %1.3.1 Giới hạn về đối tượng và chức năng
\textit{Limitations on objects:}

+ The system only supports products related to coffee and coffee culture. It cannot support other types of products.

+ The system does not support multiple languages.

+ The system does not have a mobile app version.

+ The system does not allow customers to create a wishlist.

+ The system does not support customer reviews or ratings of products.

+ The system does not provide social media integration or sharing features.\\
\textit{ Limitations on functions:}

+ The system does not support multiple payment gateways or international currencies.

+ The system does not offer real-time inventory management or automatic restocking.

+ The system does not provide advanced analytics or reporting features beyond basic sales data.

+ The system does not offer a loyalty or rewards program for customers.

+ The system does not have an automated inventory management system.

+ The system does not allow customers to track their orders in real-time.

+ The system does not provide an option for customers to cancel an order once it has been placed.

+ The system does not provide any form of loyalty program for returning customers.
\subsection{Limitations on technology} %1.3.2 Giới hạn về công nghệ
Limitations on technology depend on the functional requirements and objects of the website. \\
+ Programming language: PHP, it increases the flexibility and extend easily.\\
+ Database: MySQL, it used to store information about products, orders, customers, etc.\\
+ Framework: Laravel, it used to reduce development time and provide a better approach to code and database management.\\
+ User Interface: HTML, CSS, and JavaScript are commonly to design the website and give the best user experience.

\section{Practical significance} %1.4 ý nghĩa thực tiễn
The coffee website has great practical significance in providing an online platform for buying and selling coffee products. Customers can easily access the website to choose products, place orders, and make convenient payments. At the same time, the website also helps store owners manage products, orders, and customers more easily and effectively. Building a complete database and applying knowledge in the process of designing and implementing the website also helps enhance the store's competitiveness in the market. Therefore, the website plays an important role in improving the shopping experience for customers and improving the business efficiency of the store.
\section{Report Structure} %1.5 Bố cục báo cáo
The report is divided into 4 chapters:\\
• Chapter 1: Topic Overview\\
Introducing the topic, System description, Purpose and Scope, Practical significance and Report structure.\\
• Chapter 2: System analysis and design\\
Including Functional requirements, Non-functional requirements, Functional diagram of system (include Use-Case Diagram), Entity relationship diagram (ERD), and Data Flow Diagram (DFD).\\
• Chapter 3: Implement system\\
Describing used technologies in website to implement the system. \\
• Chapter 4: Demo System \\
Including system scenarios and demonstrating the system through screenshots. \\
• References \\
• List of Requirement Questions


